\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-04-07 paper_original.qmd
Added handwritten images that have large errors within and outside the nonlinear structure

## Decide by looking at MSE plot
num_bins_x_mnist <- 12
num_bins_y_mnist <- 15
hex_size_mnist <- 0.06

hb_obj_mnist <- hex_binning(data = pacmap_minst_scaled, x = "PaCMAP1", 
                      y = "PaCMAP2", num_bins_x = num_bins_x_mnist, 
                      num_bins_y = num_bins_y_mnist, x_start = NA, y_start = NA, 
                      buffer_x = NA, buffer_y = NA, hex_size = hex_size_mnist, col_start = "PaCMAP")

@@

model_object <- fit_highd_model( training_data = training_data_mnist, 
                                 nldr_df_with_id = pacmap_minst_scaled, 
                                 x = "PaCMAP1", y = "PaCMAP2", 
                                 num_bins_x = num_bins_x_mnist, 
                                 num_bins_y = num_bins_y_mnist, 
                                 x_start = NA, y_start = NA, 
                                 buffer_x = NA, buffer_y = NA, 
                                 hex_size = hex_size_mnist,
                                 is_rm_lwd_hex = FALSE, 
                                 benchmark_to_rm_lwd_hex = NA, 
                                 col_start_2d = "PaCMAP", 
                                 col_start_highd = "PC")

@@

<!--images that occur large error-->
```{r}
#| warning: false
#| echo: false

img_error <- error_df |> 
  dplyr::filter(total >= 10) |> 
  dplyr::pull(ID)

mnist_data <- read_rds("data/mnist/mnist_digit_1.rds")
pixels_gathered <-  mnist_data |>
  mutate(instance = row_number()) |>
  gather(pixel, value, -Label, -instance) |>
  tidyr::extract(pixel, "pixel", "(\\d+)", convert = TRUE) |>
  mutate(pixel = pixel - 2, x = pixel %% 28, y = 28 - pixel %/% 28) |>
  filter(instance %in% img_error)

@@

```{r}
#| echo: false
#| fig-cap: "Images of handwritten digit 1 which occur large model error."
#| label: fig-sampleimgerror
#| out-width: 100%
#| fig-pos: H

>>>>

## Decide by looking at MSE plot
num_bins_x_mnist <- 12
num_bins_y_mnist <- 15
hex_size_mnist <- 0.06
x_start_mnist <- -0.05773503
y_start_mnist <- -0.010

hb_obj_mnist <- hex_binning(data = pacmap_minst_scaled, x = "PaCMAP1", 
                      y = "PaCMAP2", num_bins_x = num_bins_x_mnist, 
                      num_bins_y = num_bins_y_mnist, x_start = x_start_mnist, y_start = y_start_mnist, 
                      buffer_x = NA, buffer_y = NA, hex_size = hex_size_mnist, col_start = "PaCMAP")

@@

model_object <- fit_highd_model( training_data = training_data_mnist, 
                                 nldr_df_with_id = pacmap_minst_scaled, 
                                 x = "PaCMAP1", y = "PaCMAP2", 
                                 num_bins_x = num_bins_x_mnist, 
                                 num_bins_y = num_bins_y_mnist, 
                                 x_start = x_start_mnist, y_start = y_start_mnist, 
                                 buffer_x = NA, buffer_y = NA, 
                                 hex_size = hex_size_mnist,
                                 is_rm_lwd_hex = FALSE, 
                                 benchmark_to_rm_lwd_hex = NA, 
                                 col_start_2d = "PaCMAP", 
                                 col_start_highd = "PC")

@@

<!--images that occur large error-->
<!-- within the nonlinear structure-->
```{r}
#| warning: false
#| echo: false

mnist_data <- read_rds("data/mnist/mnist_digit_1.rds")
pixels_gathered <-  mnist_data |>
  mutate(instance = row_number()) |>
  gather(pixel, value, -Label, -instance) |>
  tidyr::extract(pixel, "pixel", "(\\d+)", convert = TRUE) |>
  mutate(pixel = pixel - 2, x = pixel %% 28, y = 28 - pixel %/% 28) |>
  filter(instance %in% c(
    4699, 4785, 5173, 6671, 2186, 4636, 4882, 773, 2825, 6169, 6948, 5987, 1282, 7715, 622, 2989, 6912,
    4370, 1227, 4042, 2444, 836,
    1654))

theme_set(theme_light())
imge_error_sample_within <- pixels_gathered |> 
  ggplot(aes(x, y, fill = value)) +  
  geom_tile() +  
  facet_wrap(~ factor(instance, levels = c(
    4699, 4785, 5173, 6671, 2186, 4636, 4882, 773, 2825, 6169, 6948, 5987, 1282, 7715, 622, 2989, 6912,
    4370, 1227, 4042, 2444, 836,
    1654)), ncol = 6) +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
              axis.title.x = element_blank(), axis.title.y = element_blank(),
              axis.text.x = element_blank(), axis.ticks.x = element_blank(),
              axis.text.y = element_blank(), axis.ticks.y = element_blank(),
              panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
         legend.key.height = unit(0.25, 'cm'),
         legend.key.width = unit(0.25, 'cm'),
        strip.text = element_blank(),
        aspect.ratio = 1)
```

```{r}
#| echo: false
#| fig-cap: "Images of handwritten digit 1 which occur large model error within the nonlinear strcuture."
#| label: fig-sampleimgerrorwithin
#| out-width: 100%
#| fig-pos: H

imge_error_sample_within
```

<!--outside the nonlinear structure-->
```{r}
#| warning: false
#| echo: false

img_error <- error_df |> 
  dplyr::filter(total >= 8) |> 
  dplyr::filter((!ID %in% c(
    4699, 4785, 5173, 6671, 2186, 4636, 4882, 773, 2825, 6169, 6948, 5987, 1282, 7715, 622, 2989, 6912,
    4370, 1227, 4042, 2444, 836,
    1654))) |>
  dplyr::pull(ID)

pixels_gathered <-  mnist_data |>
  mutate(instance = row_number()) |>
  gather(pixel, value, -Label, -instance) |>
  tidyr::extract(pixel, "pixel", "(\\d+)", convert = TRUE) |>
  mutate(pixel = pixel - 2, x = pixel %% 28, y = 28 - pixel %/% 28) |>
  filter(instance %in% img_error)

@@

```{r}
#| echo: false
#| fig-cap: "Images of handwritten digit 1 which occur large model error outside the nonlinear structure."
#| label: fig-sampleimgerror
#| out-width: 100%
#| fig-pos: H

### 2024-04-07 paper_original.tex
Added handwritten images that have large errors within and outside the nonlinear structure

@@

\caption{\label{fig-sampleimgerror}Images of handwritten digit 1 which
occur large model error.}

>>>>

\includegraphics[width=1\textwidth,height=\textheight]{paper_original_files/figure-pdf/fig-sampleimgerrorwithin-1.pdf}

\caption{\label{fig-sampleimgerrorwithin}Images of handwritten digit 1
which occur large model error within the nonlinear strcuture.}

@@

\caption{\label{fig-sampleimgerror}Images of handwritten digit 1 which
occur large model error outside the nonlinear structure.}
